TUDataset: A collection of benchmark datasets for learning with graphs

### 2020-04-27 main.tex
Minor changes in text throughout.

\paragraph{Contributions} We give an overview of \textsc{TuDataset}, its unified evalution procudures, and baseline methods. Moreover, we report results on a experimental study comparing graph kernels and GNNs on a subset of the \textsc{Tud dataset}.

\section{The TUD dataset collection}

The \textsc{Tud dataset} contain over 150 datasets provided at \url{graphlearning.io}. The data loader, baseline methods, experimental evaluation tool can be installed by running \texttt{pip install tud-datasets}, see \url{XXX} for further details.

@@

Our collection of datasets covers graphs from various domains, which were provided by different authors. Therefore, they differ regarding the used graph model even within the same domain and the provided annotations, e.g., discrete or continuous node/edge attributes. We give an overview of some representative domains and graph models.

@@

@@

\subsection{Baselines}

In order to provide meaningful baselines, we provide implementation of common graph kernels was well as GNNs baselines. We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009} \nk{Das ist eine Variante mit Labeln und 3 Knoten oder?}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel, as well as the higher-order WL kernels~\cite{Mor+2019b}, in \CPP and made them accessable through the Python interface of \textsc{Tud dataset}, see \url{XXX} for further details.  Moreover, all GNN architectures implemented in PyTorch Geometric can be used as baseline as well.

Vertex kernel and edge kernel? \nk{Wäre interessant!}

\subsection{Evaluation tools}\label{eval}

In order to insure a fair and meaningful comparision between methods, we propose the following evaluation proceudres, and software tools for kernels and GNN approaches. All proposed methods can be conviently accessed from the Python interface, see \url{XXX} for further details. First, for kernels we propose the established $C$-SVM implementation \textsc{LibSvm}~\cite{Cha+11} for kernels that compute a Gram matrix, and the linear $C$-SVM implementation \textsc{LibLinear}~\cite{Fan+2008} for kernels  that can be computed based on explicit feature maps. We optimize GNNs end-to-end using \textsc{Adam}~\cite{}. Too compute accuracies and other metrics for evaluation, we propose to use $10$-fold cross validation, where we select a validation set uniformly at random from each training fold ($10\%$ of the training fold), to select hyperparamets, e.g., number of iterations, $C$ parameter, number of layers, learning rate, feature dimension, etc.

Repeat ten times?

@@

Our intention here is to provide baseline experiments, and compare graph kernels and GNNs. More precisely, we address the following questions:
\begin{description}
	\item[Q1] Are GNNs superior to graph kernels? Is there a single method that dominates?
	\item[Q2] ?
	\item[Q3] ?
\end{description}

@@

\paragraph{Datasets.} We used the \textsc{deezer\_ego\_nets}, \textsc{github\_stargazers}, \textsc{Enymes},
\textsc{Imdb-BINARY}, \textsc{Imdb-MULTI}, \textsc{Mcf-7}, \textsc{Molt-4},	\textsc{Nci1}, \textsc{Proteins},
\textsc{Reddit-Binary},	\textsc{reddit\_threads}, \textsc{twitch\_egos}, \textsc{Uacc257}. See the appendix for dataset statistics.

@@

>>>>

\paragraph{Contributions} We give an overview of \textsc{TuDataset}, its unified evalution procedures, and baseline methods. Moreover, we report results on a experimental study comparing graph kernels and GNNs on a subset of the \textsc{TuDataset}.

\section{The TUDataset collection}

The \textsc{TuDataset} contains over 120 datasets provided at \url{graphlearning.io}. The data  baseline methods and experimental evaluation tools can be installed by running \texttt{pip install tudatasets}. See the website for dataset statistics and further documentation.

@@

Our collection of datasets covers graphs from various domains, which were provided by different authors. Therefore, they differ regarding the used graph model even within the same domain and the provided annotations, e.g., discrete or continuous node and edge attributes. Here, we give an overview of some representative domains and graph models.

@@

\cm{Mention \textsc{ZINC} and the also mention size of DS, 200k}

@@

\subsection{Baselines Methods}

To provide meaningful baselines, we provide implementations of common graph kernel as well as GNNs baselines. We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{She+2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009} \nk{Das ist eine Variante mit Labeln und 3 Knoten oder? CM: Ja}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel, as well as the higher-order WL kernels~\cite{Mor+2019b}, in \CPP and made them accessible through the Python interface of \textsc{Tud dataset}, see the website for further details.  Moreover, all GNN architectures provided by PyTorch Geometric can be conveniently used as a baseline as well.

\subsection{Evaluation Methods}\label{eval}

To ensure a fair and meaningful comparison between methods, we propose the following evaluation procedures for kernels and GNN approaches. All proposed methods can be conveniently accessed from the Python interface, see the website for further details. First, for kernels we propose the established $C$-SVM implementation \textsc{LibSvm}~\cite{Cha+11} for kernels that compute a Gram matrix, and the linear $C$-SVM implementation \textsc{LibLinear}~\cite{Fan+2008} for kernels  that can be computed based on sparse, explicit feature maps. We optimize GNNs end-to-end using \textsc{Adam}~\cite{}. Too compute accuracies and MAE, we propose to use $10$-fold cross-validation, where we select a validation set uniformly at random from each training fold ($10\%$ of the training fold), to select hyperparameters, e.g., number of iterations, $C$ parameter, number of layers, feature dimension, dots Moreover, we repeat the above evaluation ten times and report standard deviations over all ten repetitions, and additionally across all one hundred runs (i.e., ten repetitions with ten folds each.).

@@

\cm{work on this}

Our intention here is to provide baseline experiments and compare graph kernels and GNNs. More precisely, we address the following questions:
\begin{description}
	\item[Q1] Are GNNs superior to graph kernels? Is there a single method that dominates?
	\item[Q2] How do kernels compare to GNNs on large-scale molecular learning tasks.
\end{description}

@@

\paragraph{Datasets.} We used the \textsc{deezer\_ego\_nets}, \textsc{github\_stargazers}, \textsc{Enymes},
\textsc{Imdb-BINARY}, \textsc{Imdb-MULTI}, \textsc{Mcf-7}, \textsc{Molt-4},	\textsc{Nci1}, \textsc{Proteins},
\textsc{Reddit-Binary},	\textsc{reddit\_threads}, \textsc{twitch\_egos}, \textsc{Uacc257}. See the website for dataset statistics.

@@

\cm{Add regression}
